%&pdflatex

\documentclass[12pt,letter]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{booktabs, caption, subcaption, float}
\usepackage[latin1]{inputenc}
\usepackage{longtable}
\usepackage{graphics}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amsfonts, amssymb, amsmath}
\usepackage{natbib, multibib}
\usepackage{theorem}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{epstopdf}
\usepackage{rotating}
\usepackage{placeins}
\usepackage[makeroom]{cancel}
\usepackage{varioref}
\usepackage{hyperref}

\setcounter{MaxMatrixCols}{10}
% TCIDATA{OutputFilter=Latex.dll} TCIDATA{Version=5.50.0.2960}
% TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
% TCIDATA{BibliographyScheme=BibTeX} TCIDATA{LastRevised=Monday, May
% 11, 2015 19:08:26} TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}

\theoremstyle{break} \theorembodyfont{\normalfont\itshape}
\newtheorem{thm}{Theorem}
\theoremstyle{break}
\theorembodyfont{\normalfont\itshape}
\newtheorem{corrollary}{Corollary} \theoremstyle{break}
\theorembodyfont{\normalfont\itshape} \newtheorem{prop}{Proposition}
\theoremstyle{break} \theorembodyfont{\normalfont\itshape}
\newtheorem{lemma}{Lemma} \theoremstyle{break}
\theorembodyfont{\normalfont\itshape} \newtheorem{algm}{Algorithm}
\theoremstyle{break} \theorembodyfont{\normalfont\itshape}
\newtheorem{definition}{Definition} \theoremstyle{break}
\theorembodyfont{\normalfont\itshape}
\newtheorem{condition}{Condition} \theoremstyle{break}
\theorembodyfont{\normalfont\itshape}

\renewcommand{\baselinestretch}{1.5}
\setlength{\hoffset}{-0.4in}
\setlength{\textwidth}{6.8in}
\setlength{\textheight}{9.3in}
\setlength{\topmargin}{-0.5in}



\begin{document}

\author{Tarek A. Hassan\thanks{\textbf{Boston University}, NBER, and
    CEPR; Postal Address: 270 Bay State Road, Boston, MA 02215, USA;
    E-mail: thassan@bu.edu.} \and
  Tony Zhang\thanks{\textbf{%
      Boston University, Questrom School of Business}; Postal Address:
    595 Commonwealth Avenue, Boston, MA 02215, USA; E-mail:
    tzhang0@bu.edu.} }

\title{The Economics of Currency Risk Premia\thanks{}}

\date{ \bigskip July 2020}

\maketitle

% +Title

\thispagestyle{empty}


\vspace{-0.7cm}


\setstretch{1.0}



\begin{abstract}
  This article reviews the literature on currency risk with a focus on
  its macroeconomic origins and implications. A growing body of
  evidence shows that countries with safer currencies enjoy
  persistently lower interest rates, a lower required return to
  capital, and accumulate relatively more capital than countries
  international investors perceive as risky. While earlier research
  has focused mainly on the role of currency risk in generating
  violations of uncovered interest parity and other financial
  anomalies, more recent evidence also points to important
  implications for the allocation of capital across countries, the
  efficacy of exchange rate stabilization policies, the sustainability
  of trade deficits, and the spill-over of shocks across borders.
\end{abstract}


\bigskip

\bigskip {\noindent \textbf{JEL classification:} }

{\noindent \textbf{Keywords:} }

\pagebreak

\setstretch{1.4} \setcounter{page}{1}


\section{Introduction}


A key tenet in economics is that the degree to which firms should be
willing to invest in a given project depends crucially on the required
rate of return to capital: a price-taking firm should install just
enough capital so that the marginal product of capital, $MPK_i$ equals
the required rate of return to
capital,$r_i$, \begin{equation}MPK_i=\underbrace{r^f+RP_i}_{
    r_i}.\label{eq_one}\end{equation} This equation is the point of
departure for many classic questions in economics. Students of asset
pricing are taught that a firm's $r_i$ has two components; a risk-free
part, $r^f$, and a risk-premium, $RP_i$, that depends on the firm's
risk characteristics. One of the classic puzzles in asset pricing is
why $RP_i$ is so large relative to $r^f$ (the equity premium puzzle).
Monetary economists are interested in the Federal Reserve's power to
manipulate $r^f$, while students of economic growth often take
differences in the $MPK_i$ as a measure of inefficiencies in the
allocation of capital across countries.

In this article we argue that recent insights from the study of
currency risk premia have important lessons for how we should think
about equation (\ref{eq_one}), and by extension, for its key
applications in asset pricing, macroeconomics, and economic growth.
The simplest, and perhaps and most important, of these lessons is that
countries differ dramatically in their risk-free interest rates. These
differences in risk-free interest rates are large (on the same order
of magnitude as the equity premium puzzle), appear to be highly
persistent over time (lasting for decades rather than years), and
cannot be explained by predictable depreciations, government default,
or differences in inflation rates. Instead, these differences in
interest rates appear intimately linked to the risk characteristics of
the country's exchange rate, and to its exchange rate regime.

Figure XX shows the difference in the risk-free interest rates of the
New Zealand Dollar and the Japanese Yen as an example (we will discuss
below how one can measure such risk-free rates and compare them across
countries). The Figure shows that the New Zealand dollar had a higher
risk-free rate than the Japanese Yen in \textit{every} month between
19XX and 20XX. On average this difference was about 6pp on an
annualized basis. When we adjust for movements in exchange rates over
the period, the difference in returns on the two countries currencies
is XXpp -- meaning that a US investors who borrowed in Yen and lent in
New Zealand Dollars on average made a return of XX percent over this
period. (For comparison, the equity premium on US stocks was about
XXpp during the same period.)

We now know that such highly persistent differences in interest rates,
similar to those between New Zealand and Japan, are common in the
data, even among developed economies. These large differences in
interest rates across countries do not appear to be equalizing over
time and translate into large differences in returns investors can
earn when investing in these currencies.

Why would $r^f$ differ permanently across countries? The emerging
consensus in the literature is that the most likely explanation are
currency risk premia -- the idea that some currencies are safer
investments than others. A useful way of thinking about this problem
is to take the perspective of a retail investor in a third country.
Banks in many countries offer savings accounts denominated in in
multiple currencies.

As it turns out, this simple intuition has a lot of support in the
data. For example, a seminal paper by Lustig and Verdelhan (2007)
shows that currencies with low interest rates on tend to appreciate
when US consumption growth is low, and depreciate when US consumption
growth is high. That is, there is direct evidence that currencies with
low interest rates appreciate when times are ``bad'', making them a
safer store of value for US investors.

In addition to this empirical evidence, the theoretical work on
currency risk has identified compelling theoretical reasons to expect
the emergence of safe-haven currencies and long-lasting differences in
interest rates. In a nutshell, currency risk premia arise naturally in
a wide range of international macro models. For example, Hassan (2013)
shows that simply allowing for some economies to be larger than others
within a standard international real business cycle model is
sufficient to generate long-term differences in interest rates between
countries, because the currencies of larger countries tend to
appreciate when world-wide output is low. That is, even within the
most canonical, frictionless, international macro models, currency
risk premia tend to arise naturally in equilibrium. Other authors have
similarly pointed to the emergence of currency premia in models with
intermediary capital constraints, trade costs, and differences in
resource endowments, among others.

A major difficulty this literature shares with a broader literature in
asset pricing is that models with conventional preferences tend to
produce risk premia that are quantitatively small. That is, although a
number of papers have identified compelling reasons why, for example,
the interest rate in Japan should be lower than that in New Zealand,
most of these models suggest that it should be lower by something on
the order of 0.06pp rather than the 6pp we measure in the data. In
this sense, the literature is running into a quantitative ``interest
differential puzzle,'' which is in some ways analogous to the equity
premium puzzle. Both puzzles fundamentally struggle with the
prediction of models with standard preferences that risk premia should
be small given the relatively small aggregate variation in consumption
growth we measure in the data. Quantitative research on currency risk
is thus a major area for future research.

We survey the rapidly growing empirical and theoretical literatures on
currency risk premia in detail in sections XX and XX. Because the
initial focus of this literature was mainly on resolving asset pricing
anomalies, many of its key papers tend to use the language of finance.
For this reason we attempted to keep this review as non-technical as
possible, focusing as much as possible on the underlying economics.

Although the literature on currency risk premia has proliferated in
recent years, it has perhaps been less successful at making clear the
relevance of these premia beyond a financial context, a gap we hope to
partially fill with this article.

Perhaps the most immediate implication of currency premia for the real
economy is for capital accumulation: If countries differ persistently
in $r^f$, then those with hither interest rates have a persistently
higher cost of capital and thus, according to (\ref{eq_one}) should
produce with relatively less capital. Returning to our example from
Figure XX, it turns out that indeed the capital-to-output ratio K/Y in
New Zealand is XX percent lower than in Japan, suggesting that,
indeed, the marginal product of capital is larger in New Zealand than
it is in Japan. More generally, countries with persistently higher
interest rates appear to have higher marginal products of capital in
the long-run. This simple insight has direct implications for several
strands of the macroeconomic literature.

The first is for the so-called Lucas-puzzle (Lucas, 1988), which
posits that


If there is indeed something to this story, it changes how we think
about central issues in macro.

1) Capital allocation 2) Efficiency calculations 3) Balance sheets of
firms in emerging markets 4) Exchange rate regimes and risk 5)
Dynamics, capital flows and risk


\section{Risk-free Interest Rates, Exchange Rates, and Currency
  returns}

Measuring Risk-free interest rates, show data

Hassan and Mano facts, Violations of UIP, Fama 84



\section{Interest Rate Differentials are Differences in Risk Premia}
\subsection{Theory}
\begin{enumerate}
\item Bare-bones model, no differences in r when risk-neutral
\item Get differences in r when risk averse
\item Pretty much any asymmetry you put into a standard macro model
  will produce differences in r
\end{enumerate}

\subsection{Evidence that currency returns depend on risk}
\begin{enumerate}
\item[-] Some currencies are safer than others
\item SIMPLE PICTURE
\item[-] Risk factors: People in finance have shown this formally
\item Brunnermeier, Nagel and Pedersen (2008)
\end{enumerate}

Continuing with our example from Figure XX, Figure XX plots the New
Zealand dollar - Japanese yen exchange rate in terms of dollars per
yen. An increase in the exchange rate indicates yen appreciation.
Figure XX highlights three distinct period of Japanese yen
appreciation, which correspond to three periods of global economic
turmoil: The early 1990s recession (1990 - 1994), the Asian financial
crisis (1997 - 1998), and the Great Recession (2007 - 2009). As a
result of the yen's tendency to appreciate during periods of economic
turmoil, investors should naturally consider the Japanese yen a safer
currency. Hence, the lower returns earned on investing in the Japanese
yen may be a result of the yen's usefulness as a hedge against bad
times. On the other hand, investing in the New Zealand dollar should
earn higher returns because the New Zealand dollar is a riskier
currency that provides none of the hedging benefits of a yen
investment.

In a seminal paper, Lustig and Verdelahn (2007) provides systematic
evidence that the currencies paying low excess returns to the U.S.
investor indeed tend compensate the U.S. investor by providing a hedge
against U.S. consumption growth risk. Their main innovation is to sort
currencies into portfolios based on the currency's interest rate, and
then explain the returns of these portfolios rather than the returns
of the currencies themselves.

This procedure of sorting financial assets into portfolios and then
explaining the returns of portfolios of assets has a long history in
empirical asset pricing. Fama French (XXXX). Intuitively, averaging
the returns of currencies within portfolios should eliminate the
diversifiable, currency-specific components of risk that are unrelated
to differences in interest rates. The remaining variation in returns
across portfolios should thus better capture risk-return trade-off
from investing in high interest rate currencies.

Menkhoff, Sarno, Schmeling, and Schrimpf (2012) show exposure to
exchange rate volatility explains cross-sectional differences in
currency returns: High interest rate currencies depreciate when global
exchange rate volatility increases. Currencies sorted into 5
portfolios based on interest rates. Low interest rate currencies
appreciate when the market is volatile.

Campbell, Meideiros and Viceira (2010) and Lustig, Roussanov and
Verdelhan (2011) show global equity volatility explains
cross-sectional differences in currency returns.


\subsection{Microfoundations}
These differences in risk premia arise naturally in macro models.
\begin{enumerate}
\item Hassan (2013)
\item Gabaix and Maggiori (2015)
\item Ready Roussanov Ward (2017)
\item Richmond (2019)
\item Farhi and Gabaix (2016)
\item Della Corte, Riddiough and Sarno (2016)
\item Tran (2013)
\item Powers (2015)
\item Wiriadinata (2020)
\end{enumerate}



If there is indeed something to this story, it changes how we think
about central issues in macro.

\section{Currency Risk and the allocation of capital across countries}
There are large differences in capital accumulation across countries:
\begin{enumerate}
\item Lucas (1988)
\item Caselli and Feyrer (2007)
\item Monge-Naranjo, Sanchez and Santaeualia-Llopis (2018)
\end{enumerate}
These differences may be explained by risk premia:
\begin{enumerate}
\item di Giovanni, Kalemli-Ozcan, Ulu, Baskaya (2019)
\item Richers (2020)
\item Hassan, Mertens and Zhang (2016)
\item David, Henriksen and Simanovska
\end{enumerate} [picture]
\section{Currency Risk and Exchange Rate Regimes}
Q: Are there other papers that argue policies can manipulate risk
premia?

\section{Dynamics}
\subsection{Quantitative literature}
\begin{enumerate}
\item Colacito and Croce (2011)
\item Gourio, Siemer and Verdelhan (2013)
\item Colacito, Croce, Ho and Howard (2018)
\end{enumerate}
\subsection{Theories written for FPP}
Heyerdahl-Larsen Statopoulous Verdelhan Backus Foresi Telmer
\subsection{Measurement of risk}
Maybe measurement of risk - implied vol - commercial indices -
newspapers - conference call transcripts
\subsection{Global financial cycle}

\section{Capital flows and the allocation puzzle}
Capital flows run counter to neo-classical model:
\begin{enumerate}
\item Gourinchas and Jeanne (2013)
\item[-] Current explanations:
\item Differences in financial development (Ju and Wei, 2006;
  Caballero, Farhi and Gouinchas, 2008; Mendoza, Quadrini and
  Rios-Rull, 2009)
\item Differences in factor utilization (Jin, 2012)
\item Differences in contracting frictions (Aguiar and Amador, 2010)
\end{enumerate}

\section{Dynamics of Currency Risk Premia}


\section{Unsorted}
\begin{enumerate}
\item Gourinchas and Rey (2007)
\item Govillot, Rey and Gourinchas (2010)
\item[-] Implications for equilibrium portfolios and global imbalances
\item Miranda-Agrippino and Rey (2020)
\item[-] Global financial cycles
\item Boccola and Lorenzoni (forthcoming)
\item[-] Debt crises
\item Du and Schreger
\item[-] Corporate balance sheets
\item[-] Special role for the dollar
\item Hassan, Mertens and Zhang (2020)
\item Burnside, Eichenbaum, Kleshchelski and Rebelo (2011)
\end{enumerate}



\end{document}